Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2025-01-13 manuscript/appendix.qmd
Hardcode appendix cross references bc it's a separate document now
Turn off line colors for now
They break in LaTeX: https://github.com/vincentarelbundock/tinytable/issues/415

all_tbl %>% 
  select(-feature_nice_paper) %>%
  mutate(across(c(mm_nice, amce_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior AMCE", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.18, 0.18, 0.40, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(all_tbl$feature_nice_paper), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE, replace = "—") %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(all_tbl$feature_nice_paper),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(
    i = tail(get_row_group_index(all_tbl$feature_nice_paper), -1),
    line = "t", line_width = 0.05, line_color = "#d3d8dc",
  ) %>%
  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

mms_trans_acc_all_tbl %>%
  select(Features = feat_acc, `Posterior EMM` = nice) %>% 
  tt(width = c(0.25, 0.2), notes = notes) %>%
  group_tt(
    i = as.character(mms_trans_acc_all_tbl$feat_transp), 
    indent = 0
  ) %>%
  style_tt(
    i = get_row_group_index(mms_trans_acc_all_tbl$feat_transp),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2, align = "c") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

trans_acc_crackdown_tbl %>%
  select(-feat_govt) %>%
  mutate(across(c(nice, diff_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior ∆", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.30, 0.18, 0.25, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(trans_acc_crackdown_tbl$feat_govt), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE) %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(trans_acc_crackdown_tbl$feat_govt),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(
    i = tail(get_row_group_index(trans_acc_crackdown_tbl$feat_govt), -1),
    line = "t", line_width = 0.05, line_color = "#d3d8dc",
  ) %>%
  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

   :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions. To avoid this, and for the sake of full transparency, we include these results in @fig-all-results and @apptbl-all-results. The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.

>>>>

all_tbl %>% 
  select(-feature_nice_paper) %>%
  mutate(across(c(mm_nice, amce_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior AMCE", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.18, 0.18, 0.40, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(all_tbl$feature_nice_paper), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE, replace = "—") %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(all_tbl$feature_nice_paper),
    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    i = tail(get_row_group_index(all_tbl$feature_nice_paper), -1),
    # line = "t", line_width = 0.05, line_color = "#d3d8dc",
    line = "t", line_width = 0.05
  ) %>%
  # style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(j = 2, line = "r", line_width = 0.1) %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

mms_trans_acc_all_tbl %>%
  select(Features = feat_acc, `Posterior EMM` = nice) %>% 
  tt(width = c(0.25, 0.2), notes = notes) %>%
  group_tt(
    i = as.character(mms_trans_acc_all_tbl$feat_transp), 
    indent = 0
  ) %>%
  style_tt(
    i = get_row_group_index(mms_trans_acc_all_tbl$feat_transp),
    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2, align = "c") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

trans_acc_crackdown_tbl %>%
  select(-feat_govt) %>%
  mutate(across(c(nice, diff_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior ∆", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.30, 0.18, 0.25, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(trans_acc_crackdown_tbl$feat_govt), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE) %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(trans_acc_crackdown_tbl$feat_govt),
    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    i = tail(get_row_group_index(trans_acc_crackdown_tbl$feat_govt), -1),
    # line = "t", line_width = 0.05, line_color = "#d3d8dc"
    line = "t", line_width = 0.05
  ) %>%
  # style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(j = 2, line = "r", line_width = 0.1) %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

@@

   :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions. To avoid this, and for the sake of full transparency, we include these results in Figure 1 in the paper and @apptbl-all-results. The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.
